---
title: "Nepal Tourism Dashboard"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll

---

```{r global, include=FALSE}
source('library.R')
source('visualize.R')
```

Home
=====================================


Home 
=====================================  
    
Column {.sidebar}
-----------------------------------------------------------------------



Column3
-----------------------------------------------------------------------

### Home 

NewPage1 {data-navmenu="Overview" data-icon="fa-list" data-orientation=columns}
=====================================     

   
Row {data-height=600}
-------------------------------------

### Chart 1



   
Row {data-height=600 }
-------------------------------------


   
### Chart 2

```{r}

```   





NewPage1 {data-navmenu="Visitors Market" data-icon="fa-list"}
=====================================     
   
Row {data-height=400}
-------------------------------------
   
### Chart 0

```{r}
tourist_arrival_average_length_stay <- read_excel("data/tourist_arrival_average_length_stay.xlsx")
```


```{r}
hchart(tourist_arrival_average_length_stay,"spline", hcaes(x = Year,y = Number),name = "Number of Tourist") 

```  

    
### Chart 1

```{r}
page_38_tourist_arrival_nationality_month <- read_excel("data/page_38_tourist_arrival_nationality_month.xlsx")
```

```{r}
num_tourist
```

Row {data-height=400}
-------------------------------------
   
### Chart 2

```{r}

ave_tourist_stay
```   
    
### Chart 3

```{r}

```

NewPage2 {data-navmenu="Visitors Market" data-icon="fa-list"}
=====================================     
   
Row {data-height=600}
-------------------------------------

### Chart 1

```{r}
```

Row {data-height=400}
-------------------------------------
   
### Chart 2

```{r}

```   
    
### Chart 3

```{r}
```



NewPage1 {data-navmenu="Region" data-icon="fa-list"}
=====================================     
   
Row {data-height=600}
-------------------------------------

### Chart 1

```{r}

```

Row {data-height=400}
-------------------------------------
   
### Chart 2

```{r}

```   
    
### Chart 3

```{r}
```


NewPage1 {data-navmenu="Industry" data-icon="fa-list"}
=====================================     
   
Row {data-height=600}
-------------------------------------

### Chart 1

```{r}
```

Row {data-height=400}
-------------------------------------
   
### Chart 2

```{r}

```   
    
### Chart 3

```{r}
```




NewPage1 {data-navmenu="Economic Context" data-icon="fa-list"}
=====================================     
   
Row {data-height=600}
-------------------------------------

### Chart 1

```{r}
```

Row {data-height=400}
-------------------------------------
   
### Chart 2

```{r}

```   
    
### Chart 3

```{r}
```

